Detailed structure of phospholipid bilayers with negatively charged lipids and salt concentrations from molecular dynamics simulations including the effects of electronic polarization

### 2019-05-13 Manuscript/manuscript.tex
Improved table with the list of simulations

\begin{table*}[tbp]
\centering
\caption{  List of MD simulations reporting their respective
           added buffer concentrations,
           amounts of individual molecules,
           and the deployed models.
           The fatty acid chains for all lipids are plamitoyl (sn-1) and oleoyl (sn-2).
         }\label{tbl:sim-list}
\begin{tabular}{l | r r r r | r r | c c }
                          &  \multicolumn{4}{c}{added buffer concentration / mM}    & \multicolumn{2}{c}{no. molecules} &  \multicolumn{2}{c}{simulated with model}  \\
PC:PS (ratio)/counterions &  \ce{K^+}  &  \ce{Na^+} & \ce{Ca^{2+}} & \ce{Cl^-}      & \ce{H2O} &  PC:PS                 &  ECC-lipids  &  Lipid17    \\
  \hline
PC:PS (0:1)/K+   &      0  &      0  &      0  &      0  &  3600  &  0:72  &  X  &  X  \\ 
PC:PS (0:1)/Na+  &      0  &      0  &      0  &      0  &  3600  &  0:72  &  X  &  X  \\ 
  \hline
PC:PS (10:1)/K+  &      0  &      0  &      0  &      0  &  3600  &  60:6  &  X  &  -  \\ 
PC:PS (10:1)/Na+ &      0  &      0  &      0  &      0  &  3600  &  60:6  &  X  &  -  \\ 
  \hline
PC:PS (1:1)/K+   &      0  &      0  &      0  &      0  &  5253  &  64:64  &  X  &  X  \\ 
PC:PS (1:1)/Na+  &      0  &      0  &      0  &      0  &  5253  &  64:64  &  X  &  X  \\ 
  \hline
PC:PS (4:1)/K+   &      0  &      0  &      0  &      0  &  3600  &  48:12  &  X  &  -  \\ 
PC:PS (4:1)/Na+  &      0  &      0  &      0  &      0  &  3600  &  48:12  &  X  &  -  \\ 
  \hline
PC:PS (5:1)/K+   &      0  &      0  &      0  &      0  &  3600  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &      0  &      0  &  3600  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &     78  &     78  &  3561  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &    125  &    125  &  3561  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &    202  &    202  &  3561  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &    409  &    409  &  3522  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &    621  &    621  &  3483  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &    621  &      0  &    621  &  3483  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &   1510  &      0  &   1510  &  3377  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &   3002  &      0  &   3002  &  3213  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &    621  &      0  &      0  &    621  &  3483  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &   1510  &      0  &      0  &   1510  &  3377  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &   3002  &      0  &      0  &   3002  &  3213  &  60:12  &  X  &  X  \\ 
  \hline
\end{tabular}
\end{table*}

>>>>

\begin{table*}[tbp]
\centering
\caption{  List of MD simulations reporting their respective
           lipid composition,
           used counterions,
           added buffer concentrations,
           amounts of individual molecules,
           and the deployed models.
           The fatty acid chains for all lipids are plamitoyl (sn-1) and oleoyl (sn-2).
         }\label{tbl:sim-list}
\begin{tabular}{l l | r r r r | r r | c c }
   \multicolumn{2}{c}{ }  &  \multicolumn{4}{c}{added buffer conc. / mM}    & \multicolumn{2}{c}{no. molecules} &  \multicolumn{2}{c}{simulated with model}  \\
PC:PS ratio & counterions &  \ce{K^+}  &  \ce{Na^+} & \ce{Ca^{2+}} & \ce{Cl^-}      & \ce{H2O} &  PC:PS                 &  ECC-lipids  &  Lipid17    \\
  \hline
0:1 & \ce{K^+}   &      0  &      0  &      0  &      0  &  3600  &  0:72  &  X  &  X  \\ 
0:1 & \ce{Na^+}  &      0  &      0  &      0  &      0  &  3600  &  0:72  &  X  &  X  \\ 
  \hline
10:1 & \ce{K^+}  &      0  &      0  &      0  &      0  &  3600  &  60:6  &  X  &  -  \\ 
10:1 & \ce{Na^+} &      0  &      0  &      0  &      0  &  3600  &  60:6  &  X  &  -  \\ 
  \hline
1:1 & \ce{K^+}   &      0  &      0  &      0  &      0  &  5253  &  64:64  &  X  &  X  \\ 
1:1 & \ce{Na^+}  &      0  &      0  &      0  &      0  &  5253  &  64:64  &  X  &  X  \\ 
  \hline
4:1 & \ce{K^+}   &      0  &      0  &      0  &      0  &  3600  &  48:12  &  X  &  -  \\ 
4:1 & \ce{Na^+}  &      0  &      0  &      0  &      0  &  3600  &  48:12  &  X  &  -  \\ 
  \hline
5:1 & \ce{K^+}   &      0  &      0  &      0  &      0  &  3600  &  60:12  &  X  &  X  \\ 
5:1 & \ce{Na^+}  &      0  &      0  &      0  &      0  &  3600  &  60:12  &  X  &  X  \\ 
5:1 & \ce{Na^+}  &      0  &      0  &     78  &     78  &  3561  &  60:12  &  X  &  X  \\ 
5:1 & \ce{Na^+}  &      0  &      0  &    125  &    125  &  3561  &  60:12  &  X  &  X  \\ 
5:1 & \ce{Na^+}  &      0  &      0  &    202  &    202  &  3561  &  60:12  &  X  &  X  \\ 
5:1 & \ce{Na^+}  &      0  &      0  &    409  &    409  &  3522  &  60:12  &  X  &  X  \\ 
5:1 & \ce{Na^+}  &      0  &      0  &    621  &    621  &  3483  &  60:12  &  X  &  X  \\ 
5:1 & \ce{Na^+}  &      0  &    621  &      0  &    621  &  3483  &  60:12  &  X  &  X  \\ 
5:1 & \ce{Na^+}  &      0  &   1510  &      0  &   1510  &  3377  &  60:12  &  X  &  X  \\ 
5:1 & \ce{Na^+}  &      0  &   3002  &      0  &   3002  &  3213  &  60:12  &  X  &  X  \\ 
5:1 & \ce{Na^+}  &    621  &      0  &      0  &    621  &  3483  &  60:12  &  X  &  X  \\ 
5:1 & \ce{Na^+}  &   1510  &      0  &      0  &   1510  &  3377  &  60:12  &  X  &  X  \\ 
5:1 & \ce{Na^+}  &   3002  &      0  &      0  &   3002  &  3213  &  60:12  &  X  &  X  \\ 
  \hline
\end{tabular}
\end{table*}
